\chapter{Introduction}

As part of my courses at Polytech Nantes, the graduate school of engineering og the University of Nantes, I did a three months abroad internship. 

~~

The intership goal is to demark each Polytech students by travelling across the world, and to apprehend the professionnal world of a laboratory or a company.

~~

I realised my forth year internship at the University of Petroleum and Energy Studies (UPES), in the Bidholi campus, which is based in India, at the Uttarakhand state.

~~

I was affected in a new project related to the autonomous navigation of a robot in an unknown environment. My mission involved the generation of a 3D map, which will be used in the robot's navigation algorithm.

~~

I wanted to try this internship in India in order to discover another and totally different culture from mine. Moreover, the inthership proposed byt the UPES was a good opportunity, as Polytech Nantes and the UPES have a new partnership together, it facilitated the integration in the university, the administrative process, and the school exchange. 

~~

The purpose of this report is to describe what I have done during my internship at the UPES. First, I will present you the University of Petroleum and Energy Studies in a more detailed way. Then I will talk about the mission that was given to me. I will then expose to you the work I have done and the results I got. I will also talk about how we organized our work schedule. Finally, I will conclude with what I learned from this internship.
