\chapter{The project and my mission}

This chapter will introduce the project I was assigned, and the mission I was given.

\section{The project}

This new project involves designing an autonomus navigation algorithm for a robot, which will be moving in an unknown environment. 

~~

A robot is a machine that can do the work of a person, automatically or by being controlled (i.e. a computer or a person). 
In this project, a robot is defined as a mechanical device that has wheels allowing it to move freely in his surrounding. 
In order to detect and take note of the surroundings, it is also required that the robot is equiped with cameras ans sensors. 
As for now, the \gls{UPES} doesn't have the robot for the moment. 

~~

The robot will have to move in an environment from a position to another. Both of those two positions are known, but the path to take in order to move from one to another is not. Obstacles could be found in this environment (i.e. everything that could be on the way of the robot and block it, like rocks, walls or holes in the ground). 

~~

In general, navigation can be divided into two parts, whether it is performed in a knowned or an unknowned enviromnent. They differ by the knowleadge about the environment the agent possess (in our case, the robot) : 
\begin{description}
	\item[Known environment] the agent know the outcome of every action it can take. For a robot, it means that it knows the path to take and all obstacle's positions it can encounter in advance 
	\item[Unknown environment] 
\end{description}
In our case, the robot will explore in an unknown environment, for example it could explore and search into a submarin field, or the planet Mars. 




~~

In other words, the objective of the reseach is "To design and develop a self-learning algorithm for an autonomous moving system equipped with 3D vision technique" \cite{bib:niharika}.



\section{My mission in this project}
